I would like to first express my sincere appreciation to my Ph.D. advisor, Prof. Yezhou Yang. Yezhou is a wise and thoughtful researcher and deeply influenced my whole Ph.D. journey. He always gives great encouragement whenever I'm confronted with difficulties and I'm always motivated by his persistent passion and curiosity towards science. When my Ph.D.  journey rises \& falls and grinds me a lot, Yezhou's spirits always light me up. 

I would also like to thank Dr. Shu Kong, he gave me great mentorship for my research in my early Ph.D. days and profoundly taught me how to become an independent researcher.

Special thanks to all my mentors in the Microsoft Florence team: Jianfeng Wang, Xiaowei Hu, Zhe Gan, and Lei Zhang. I also send my sincerest gratitude to the group leaders Lijuan Wang and Zicheng Liu. Despite the great challenges brought by the pandemic, I've spent two wonderful years with the Florence team remotely and we produced great works in the Vision and Language domain. I really enjoyed the collaboration with them all and none of our accomplishments can be finished without the trust from Lijuan and Zicheng and also the valuable guidance from the team.

I spent my five wonderful years at ASU with lots of friends and peers: Tejas Gokhale, Man Luo, Xin Ye, Mohammad, Varun, Sheng, Changhoon, Pratyay, Kaize, Rudra, Huiliang, Yikang, Shibin, Zhe Wang, and Dawei. And congratulations to Joshua and his wife for becoming parents, best wishes for the new life! I also thank my friends Jian Kang, Tianlu, Lu Cheng, Chengxi Ye, and Tianshu Yu for their support and help.

I acknowledge the National Science Foundation under the Robust Intelligence Program
(1816039 and 1750082) for their financial support. I also acknowledge the support from the DARPA KAIROS program (LESTAT project), the DARPA SAIL-ON program, and ONR award N00014-20-1-2332.

Meanwhile, I appreciate all my Ph.D. committees, Prof. Chitta Baral, Prof. Huan Liu, and Prof. Zicheng Liu: they give me consistent support and precious suggestions for my dissertation prospectus and I'm more than lucky to be able to be guided by these amazing professors!

To this end, to my beloved family, and Miss Meijia, thank you for your eight-year companion, I love you all.

